---
title: "Working Papers"
output: html_document
---

<div class="post">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***

## Private vs. Public Welfare

I had to defend this paper in order to complete my Master's program at the University of Georgia. The paper looks at an area of public policy that is rarely discussed by political scientists: private welfare. The little research that has been done in this area shows that every major country in the world finances their welfare state, to varying degrees, using private means. After acknowledging the prevalence of private welfare, I began to wonder why some countries employ more private welfare than others, which is the question what this paper attempts to answer.

***

```{r knitr, echo=FALSE, cache=TRUE}
knitr::include_graphics("welfare-paper.pdf")
```

***

```{css, echo=FALSE}
.post {
  width: 500px;
  margin-left: auto;
  margin-right: auto;
}

html body div.container-fluid.main-container p embed {
  width: 600px;
  height: 700px;
  border: 1px solid #c3c3c3;
  margin-left: auto;
  margin-right: auto;
  ALIGN=CENTER;
}

html body div.container-fluid.main-container p {
  font: 16px Georgia, serif;
  padding-right: 0px;
  padding-left: 0px;
}
```